MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-07-15 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

With a group of web services having identical or similar functionalists, QoS metrics provide nonfunctional characteristics for the optimal candidate selection. Web service quality metrics have been presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}, we have adopted the most representative QoS properties of web services which highly influence the utility of web services.

@@

  \item \emph{Throughput} is the rate at which a service can process requests. QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity. Throughput is a real number in the range $[0, 1]$.

	\item \emph{Availability} is the percentage of time that a service is operating.
	The probability that the service operation is accessible. Availability is also a real number in the range $[0, 1]$.

	\item \emph{Execution Time} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in seconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer.

@@

>>>>

With a group of web services having identical or similar functionalists, QoS metrics provide nonfunctional characteristics for the optimal candidate selection. Web service quality metrics have been presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}, we have adopted the most representative QoS properties of web services which highly influence the utility of web services. 
%We refer to a typical web service as ws_{i}.

@@

  \item \emph{Throughput $(Th_{i})$} is the rate at which a service can process requests. QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity. Throughput is a positive real number.

	\item \emph{Availability $(A_{i})$} is the percentage of time that a service is operating.
	The probability that the service operation is accessible. Availability is also a real number in the range $[0, 1]$.

	\item \emph{Execution Time $(Rt_{i})$} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in milliseconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer.

@@

A community of web services are abstracted as a standard web service providing services sharing same internal and external features mentioned for web services. Inside, they adopt different protocols to manage the community, however other web services or end users can communicate with communities of web services, using standard protocols and inner details will be encapsulated for their clients.

\subsection{Task Distribution}

As mentioned in Section \ref{s:wsc}, communities 
are robust service providers with well established market share
and reputation. By maintaining their reputation and performance,
they attract end users which choose them as service providers to
perform their tasks. The community coordinator is characterized by a
request rate (also called input rate) $(R_C)$ from users. Each web
service comes with a given QoS ($QoS_{ws}$) from which the
throughput $Th_{ws}$ is excluded. Throughput is the average rate
of tasks a web service can perform per time unit. Its exclusion
from $QoS_{ws}$ allows us to build our analysis on the particular
value of $Th_{ws}$. Thus, web services perform tasks with an
average output quality of $QoS_{ws}$ and a throughput rate of
$Th_{ws}$.

The community coordinator uses a slightly modified \emph{weighted fair
queuing} method to distribute tasks among its members. The goal is
to allocate incoming tasks to web services with a rate matching
the throughput value of $Th_{ws}$. In the \emph{weighted fair
queuing} method, \emph{all} the input flow is multiplexed along
different paths, however in our case if the request rate $(R_C)$
of the community is more than the summation of throughput values
of the web services in the community, some of the input tasks will
be queued and served with delay. Thus, the amount of tasks
performed by the community is $\sum_{ws}{Th_{ws}}$ when
$\sum_{ws}{Th_{ws}} \leq R_{C}$. However, when the input rate
$(R_C)$ of the community is less than the summation of throughput
values of the web services in the community,
%the community has more web services having more total throughput value than community's request rate
the \emph{weighted fair queuing} algorithm assigns a weighted task
rate of $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each
web service ($ws$), so that the total rate of tasks being
performed is $R_C$, the community's request rate.

While distributing tasks, the community coordinator can verify the
performance, throughput and quality of service of tasks being
performed by web services. The community coordinator can recognize if those web
services are capable of doing the amount of tasks they advertised.
If for any reason there is a decline in the quality metric or
throughput, the coordinator will announce the new parameters, which
will be considered as benchmark for future performance
calculations, and penalize the suspicious web services. In this
way, players will have incentive to truthfully reveal their real
capabilities in order to profit best from the community and to
avoid being penalized. In addition, the system should be dynamic
enough to detect and react to web services quality metrics
variation as over time web service metrics may degrade or improve,
a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

\subsection{Community Revenue (Utility)}

The communities and web services earn revenue by performing tasks.
The total gain is function of quality ($QoS_{ws}$) and throughput
($Th_{ws}$) of tasks being performed. As mentioned in Section
\ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain
aggregation function of the parameters considered in Table
\ref{qosws}. We have adopted a linear equal weight average over
all QoS parameters listed in Table \ref{qosws} excluding the
$Throughput$ and $Cost$ parameters. A community has the option to
weigh specific QoS parameters depending on the expectations of
their clients.

The maximum potential output of a community $C$ $(PO(C))$  is an
aggregation of the number of performed tasks $T_{ws}$ times the
quality of service $QoS_{ws}$ for each web service member of the
community:

\begin{equation}
PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
\end{equation}

If the summation of throughput values ($Th_{ws}$) of community
members exceeds the input task rate of the community ($R_C$), the
community cannot perform at its maximum potential. This situation
denotes the case when the community has more web services than it
needs to perform the input task load. Thus, the actual output has
to be normalized to the amount of tasks being performed.

\begin{equation}\label{out_c}
Out(C) = \left\{
  \begin{array}{l l}
    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
  \end{array} \right.
\end{equation}

The revenue function of the web service community is a linear
function of $Out(C)$ with a positive constant multiplier. The
worth of a community is set to the output the community can
generate, i.e., $v(C) = Out(C)$.
